### 2012-03-27 exam4/2.tex
Final touches.

\emph{Good luck!}
\end{minipage}\hfil\begin{minipage}[t]{6cm}
\rule{1cm}{0pt}\begin{tabular}{|c|l|@{/}r|}
\hline
{\bf Problem} & Points & out of \\ \hline
1 & & 15\\ \hline
2 & & 22\\ \hline
3 & & ??\\ \hline
4 & & ??\\ \hline
5 & & 20\\ \hline
%% Extra & & 5 \\ \hline
{\bf Total} & & ?? \\ \hline
%{\bf Base}  & \multicolumn{2}{l|}{{\bf 56}} \\ \hline
\end{tabular}
\end{minipage}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem}\pts{22}

Design a \verb|TreeVisitor| interface for 2/3-trees, and implement the
\verb|visit| method in all of your classes from the previous problem.
Make sure you design the interfaces and methods so that a visitor can
return any type of data.

@@

Design the \verb|CountVisitor| class, which counts the number of
leaves in a 2/3-tree (there are 6 in the given example.)

@@

Design the \verb|LongestVisitor| class, which produces the longest
\verb|String| in a 2/3-tree.  The longest string in the example is
\verb|"Rhinocerous"|.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem} \pts{??}

@@

\newpage
\noindent
Part (A): Implement the omitted {\tt same} method that compares this
unordered pair to a given unordered pair.  This method should work
regardless of the order of the pair, so for example {\tt new
  UnPair<Integer>(3,4)} is the same (according to {\tt same}) as {\tt
  new UnPair<Integer>(4,3)}.

\newpage
\noindent
Part (B): Assuming {\tt same} and {\tt equals} work as expected, is
the given {\tt hashCode} method valid?  That is, does it satisfy or
violate the law of {\tt hashCode}?  If it is valid, give an argument
for \emph{why}.  If it is not, give a counter-example to the law of
{\tt hashCode}.
\end{problem}
\newpage

\begin{problem} \pts{??}

@@

@@

Iterators are an extremely useful concept.  In particular, they aren't
limited to iterating over the contents of data structures such as {\tt
ArrayList}s.  We can also construct iterators directly, for sequences
we are interested in.

@@

Design the class {\tt RangeIterator}, which takes two {\tt Integer}s
as constructor arguments, and iterates over all of the {\tt Integer}s
between them, including \emph{both} end points.  {\tt RangeIterator}
must implement the {\tt Iterator} interface, given below.

\begin{verbatim}
interface Iterator<T> {
  Boolean hasNext();
  T next();
  // The Java definition of Iterator includes the remove method.
  // You do *not* need to implement remove.
}
\end{verbatim}

@@

\noindent
Recall our definition of function objects:
\begin{verbatim}
interface Function<T,U> {
  U call(T x);
}
\end{verbatim}
\noindent
Define the {\tt Square} class, which is a \verb|Function| that squares
\verb|Integer|s.

@@

Using this interface, design and implement the {\tt MapIterator}
class, which takes a \verb|Function| and an \verb|Iterator| as
arguments, and iterates over the values produced by applying the
function to each result produced by the iterator.

@@

\noindent
Now design the method \verb|sumSquares|, which takes two
\verb|Integer|s, and uses the classes you've just defined, along with
a \verb|for| or \verb|while| loop, to compute the sum of the squares
of all the numbers between the given \verb|Integer|s, inclusive.

@@

//> Tests 1pt
sumSquares(1,2) -> 5
sumSquares(0,0) -> 0
sumSquares(10,10) -> 100
\end{verbatim}
\end{solution}
\else
\newpage
[Here is some more space for the previous problem.]
\fi

>>>>

\emph{Good luck!}
\end{minipage}\hfil\begin{minipage}[t]{6cm}
\rule{1cm}{0pt}\begin{tabular}{|c|l|@{/}r|}
\hline
{\bf Problem} & Points & out of \\ \hline
1 & & 15\\ \hline
2 & & 22\\ \hline
3 & & 15\\ \hline
4 & & 15\\ \hline
5 & & 20\\ \hline
%% Extra & & 5 \\ \hline
{\bf Total} & & 87 \\ \hline
%{\bf Base}  & \multicolumn{2}{l|}{{\bf 56}} \\ \hline
\end{tabular}
\end{minipage}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem}\pts{22}
\
\begin{enumerate}
\item Design a \verb|TreeVisitor| interface for 2/3-trees, and implement the
\verb|visit| method in all of your classes from the previous problem.
Make sure you design the interfaces and methods so that a visitor can
return any type of data.

@@

\item Design the \verb|CountVisitor| class, which counts the number of
leaves in a 2/3-tree (there are 6 in the given example.)

@@

\item Design the \verb|LongestVisitor| class, which produces the longest
\verb|String| in a 2/3-tree.  The longest string in the example is
\verb|"Rhinocerous"|.  
\end{enumerate}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem} \pts{15}

@@

\newpage
\begin{enumerate}
\item Implement the omitted {\tt same} method that compares this
  unordered pair to a given unordered pair.  This method should work
  regardless of the order of the pair, so for example {\tt new
    UnPair<Integer>(3,4)} is the same (according to {\tt same}) as
  {\tt new UnPair<Integer>(4,3)}.

\newpage
\item Assuming {\tt same} and {\tt equals} work as expected, is
the given {\tt hashCode} method valid?  That is, does it satisfy or
violate the law of {\tt hashCode}?  If it is valid, give an argument
for \emph{why}.  If it is not, give a counter-example to the law of
{\tt hashCode}.
\end{enumerate}
\end{problem}
\newpage

\begin{problem} \pts{15}

@@

\newpage
[Here is some more space for the previous problem.]

@@

Iterators are an extremely useful concept.  In particular, they aren't
limited to iterating over the contents of data structures such as {\tt
  ArrayList}s.  We can also construct iterators directly for sequences
we are interested in.

@@

\begin{enumerate}
\item Design the class {\tt RangeIterator}, which takes two {\tt Integer}s
as constructor arguments, and iterates over all of the {\tt Integer}s
between them, including \emph{both} end points.  {\tt RangeIterator}
must implement the {\tt Iterator} interface, given below.

\begin{verbatim}
interface Iterator<T> {
  Boolean hasNext();
  T next();
  // Java requires an Iterator to define remove,
  // but you do *not* need to implement remove.
}
\end{verbatim}

\newpage
[Here is some more space for the previous problem.]

@@

\item
Recall our definition of function objects:
\begin{verbatim}
interface Function<T,U> {
  U call(T x);
}
\end{verbatim}
\noindent
Define the {\tt Square} class, which is a \verb|Function| that squares
\verb|Integer|s.

@@

\item Using this interface, design and implement the {\tt MapIterator}
class, which takes a \verb|Function| and an \verb|Iterator| as
arguments, and iterates over the values produced by applying the
function to each result produced by the iterator.

@@

\noindent
\item Now design the method \verb|sumSquares|, which takes two
\verb|Integer|s, and uses the classes you've just defined, along with
a \verb|for| or \verb|while| loop, to compute the sum of the squares
of all the numbers between the given \verb|Integer|s, inclusive.

@@

//> Tests 1pt
sumSquares(1,2) -> 5
sumSquares(0,0) -> 0
sumSquares(10,10) -> 100
\end{verbatim}
\end{solution}
\else
\newpage
[Here is some more space for the previous problem.]
\fi
\end{enumerate}
\end{problem}
